% !TEX root = ../report.tex

\begin{description}
 \item[1. At least one door of a sluice is closed at any point in time]\mbox{}\\
$
[true^*]\forall s:Sluice.\forall d:Door.[openDoor(d, s).\overline{closeDoor(d, s)}^*.openDoor(d, s)]false
$


 \item[2. No robot may interact with a sluice whenever its access door is closed]\mbox{}\\
$
[true^*]\forall s:Sluice.(  \newline
\phantom{=} [closeDoor(outsideDoor, s).(\overline{openDoor(outsideDoor, s)}^*.( \newline
\phantom{==} move(RI, sluicePlace(s)) \cup move(sluicePlace(s), RI) \cup \newline
\phantom{==} move(RO, sluicePlace(s)) \cup move(sluicePlace(s), RO) \newline
\phantom{=} )]false \wedge \newline
\phantom{=} [closeDoor(insideDoor, s).(\overline{openDoor(insideDoor, s)}^*.( \newline
\phantom{==} move(I, sluicePlace(s)) \cup move(sluicePlace(s), I) \cup \newline
\phantom{==} move(O, sluicePlace(s)) \cup move(sluicePlace(s), O) \newline
\phantom{=} )]false \newline
)
$
 
 \item[3. Any wafer in the system will eventually be processed]

	\begin{align*}
		&[true^*.detectInputWafer(s)]true\\
		&[true^*.detectInputWafer(s).\overline{detectInputWafer(t)^*}]false\\
		&[true^*.detectInputWafer(s).\overline{move(RI, a)^*}]false\\
		&[true^*.move(RI, a).\overline{move(b,RO)^*}]false
	\end{align*}

 
 \item[4. Internal racks, sluices and the projector each contain at most one wafer]
    
    For all $p$, there exist $p_1, p_2, p_3$:
	\begin{align*}
		&[true^*.move(p_1, p).\overline{move(p,p_3)^*}.move(p_2,p)]false
	\end{align*}

 
 \item[5. When the projector is at work, no interaction with the wafer is permissible]
 	\begin{align*}
 		&[true^*.beginProject().\overline{endProject()^*}.move(P,O)]false
	\end{align*}
	
 \item[6. A sluice door cannot open until the pressure on both sides is equal]
	\begin{align*}
		&[true^*.vacuum(s).stopPumping(s).\overline{readAirPressure(s,0)^*}.openInside(s)]false \\
		&[true^*.deVacuum(s).stopPumping(s).\overline{readAirPressure(s,1)^*}.openOutside(s)]false \\
	\end{align*}
	
 \item[7. Sluice pumps cannot operate until both of its doors are closed]
 
  For $s \in \{sluice1, sluice2\}:$
 \begin{align*}
		&[true^*.openInside(s).\overline{closeInside(s)^*}.vacuum(s)]false \\
		&[true^*.openInside(s).\overline{closeInside(s)^*}.deVacuum(s)]false \\
		&[true^*.openOutside(s).\overline{closeOutside(s)^*}.vacuum(s)]false \\
		&[true^*.openOutside(s).\overline{closeOutside(s)^*}.deVacuum(s)]false \\
	\end{align*}

 \item[8. No robot can place a projected wafer in $RI$]\mbox{}\\
$
[true^* \cdot detectInputWafer]\\
\nu X(position:Place=RI, projecting:Bool=false, projected:Bool=false)\\
.\forall a,b:Place.[move(a,b)]X(if(a \approx position, b, position), projecting \wedge a \not \approx position, projected)\\
\wedge [\overline{\exists a,b:Place.move(a,b) \cup beginProject \cup endProject)}]X(position, projecting, projected)\\
\wedge [beginProject]X(position, position \approx P, projected)\\
\wedge [endProject]X(position, false, projected \vee (projecting \wedge position \approx P))\\
\wedge (position \approx RI \implies \neg projected)
$
 \item[9. No robot can place an unprojected wafer in $RO$] \mbox{}\\
$
[true^* \cdot detectInputWafer]\\
\nu X(position:Place=RI, projecting:Bool=false, projected:Bool=false)\\
.\forall a,b:Place.[move(a,b)]X(if(a \approx position, b, position), projecting \wedge a \not \approx position, projected)\\
\wedge [\overline{\exists a,b:Place.move(a,b) \cup beginProject \cup endProject)}]X(position, projecting, projected)\\
\wedge [beginProject]X(position, position \approx P, projected)\\
\wedge [endProject]X(position, false, projected \vee (projecting \wedge position \approx P))\\
\wedge (position \approx RO \implies projected)
$

 \item[10. No robot can take a wafer from $RO$]

\[
	\forall p:Place . [true^* \cdot move(RO, p)]false
\]

\end{description}
